The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-19 RET_Hosts_IR.tex
Updates from Overleaf

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
%Co-authors:
\newcommand{\phil}[1]{\color{red}#1 \color{black}}
\newcommand{\mike}[1]{\color{cyan}#1 \color{black}}
\newcommand{\replychris}[1]{\color{magenta}#1 \color{black}}
\newcommand{\replylluis}[1]{\color{green}#1 \color{black}}
\newcommand{\comment}[1]{\textbf{[#1]}} %comments

@@

 Along with observations of the transients themselves, host galaxies are frequently-used laboratories from which strong inferences about the progenitor stars and explosion mechanisms can be made. CCSNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars. There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties. On average, SESNe reside in galaxies with higher specific star-formation rate\replychris{s} (sSFRs; \citealt{James2006,Kelly2008}), \replylluis{while studies of the local environments tend to show SESNe to explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Galbany2018}}. More extreme events tend to occur in galaxies low in mass and high in sSFR, with both GRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.

@@

The order of the paper is as follows: \replychris{in Section \ref{sec:sample} we introduce the full DES RET sample and describe the host galaxy observations in Section \ref{sec:obs}. The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:disc}) and conclusion (Section \ref{sec:conc}).}
Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters H$0=70$ km~s$^{-1}$ and $\Omega_{\textrm{M}}=0.3$.

@@

DES13C3avkj    & 51.97076 & -27.52792 & 24.07937 & 0.04534 &    $^c$ &      OzDES &             - \\
DES13X3gms     & 35.80095 &  -4.49384 & 23.02264 & 0.06436 & 0.64792 &      OzDES &       6.58333 \\
DES13C1tgd     & 54.06436 & -27.63867 & 20.30968 & 0.05848 & 0.19647 &      OzDES &      10.16667 \\
DES13C3abtt    & 52.62108 & -28.16151 & 21.50529 & 0.03508 &    $^d$ &          - &             - \\
DES13S2wxf     & 41.61268 &  -0.02634 & 21.31219 & 0.03266 & 0.56985 &      OzDES &       5.41639 \\
DES13X1hav     & 35.03245 &  -5.11022 & 23.63452 & 0.07752 & 0.58236 &      OzDES &       4.00000 \\
DES13C3smn     & 51.97112 & -28.08362 & 25.30041 & 0.06023 &    $^c$ &      OzDES &             - \\
DES13X3nyg     & 36.99228 &  -3.91327 & 23.38744 & 0.06173 & 0.71205 &      OzDES &      45.50000 \\
DES13X3gmd     & 36.50409 &  -4.21949 & 22.90614 & 0.05419 & 0.78082 &      OzDES &      13.91667 \\
DES13C3bcok    & 53.02711 & -28.62476 & 18.61674 & 0.02560 & 0.34577 &  LADUMA &               \\
DES13X3afjd    & 37.00386 &  -4.58049 & 20.75298 & 0.05737 &    $^d$ &          - &             - \\
DES13C1acmt    & 54.32925 & -26.83371 & 23.18742 & 0.04422 &    $^c$ &      OzDES &             - \\
DES13X3kgm     & 36.50380 &  -4.86636 & 26.46803 & 0.18709 &    $^d$ &          - &             - \\
DES13C3uig     & 52.94416 & -27.58544 & 22.17966 & 0.03116 & 0.67346 &       ACES &               \\
DES13C3nxi     & 51.96356 & -28.35720 & 24.99276 & 0.05177 &    $^c$ &      OzDES &             - \\
DES13C3asvu    & 52.83670 & -27.36071 & 22.46669 & 0.02874 &    $^d$ &          - &             - \\
DES13X3pby     & 36.33330 &  -5.31408 & 23.82628 & 0.04671 &    $^c$ &      OzDES &             - \\
DES13X3aakf    & 35.71205 &  -4.69915 & 25.47453 & 0.09478 &    $^c$ &      OzDES &             - \\
DES13X2wvv     & 34.86526 &  -6.71603 & 21.89573 & 0.02567 & 0.47503 &      OzDES &       4.50000 \\
DES13X2oyb     & 35.31056 &  -5.67893 & 22.91589 & 0.06115 &    $^c$ &      OzDES &             - \\
DES13X3alnb    & 37.18496 &  -5.14232 & 25.04147 & 0.06167 &    $^c$ &      OzDES &             - \\
DES15X3atd     & 35.84011 &  -4.29142 & 23.87686 & 0.05432 &    $^c$ &      OzDES &             - \\
DES14S2anq     & 41.27776 &  -0.74529 & 17.57076 & 0.03648 & 0.05211 &      OzDES &       0.75000 \\
DES14E2xsm     &  9.67624 & -43.58736 & 23.39163 & 0.04458 &    $^c$ &      OzDES &             - \\
DES14X1bnh     & 33.74902 &  -4.79254 & 21.95260 & 0.03597 & 0.82982 &      OzDES &       3.50000 \\
DES14E1aqi     &  8.73970 & -43.40182 & 25.61559 & 0.23708 &    $^d$ &          - &             - \\
DES15S1fli     & 43.18790 &  -0.88620 & 20.98517 & 0.02950 & 0.44739 &      OzDES &       2.33333 \\
DES14C3gzj     & 52.57168 & -28.14019 & 26.04181 & 0.10494 &    $^d$ &          - &             - \\
DES14X3pko     & 36.90824 &  -3.69642 & 24.48291 & 0.06326 &    $^d$ &          - &             - \\
DES15S1fll     & 42.78846 &  -0.19747 & 20.95918 & 0.03719 & 0.22647 &      OzDES &       0.66667 \\
DES14C1jnd     & 54.35153 & -27.49300 & 24.33143 & 0.08524 &    $^c$ &      OzDES &             - \\
DES14X3pkl     & 37.21103 &  -4.80741 & 22.40853 & 0.06026 & 0.29537 &      OzDES &       5.16667 \\
DES13X3npb     & 36.64218 &  -4.13381 & 20.79328 & 0.05336 & 0.49542 &      OzDES &       5.16667 \\
DES15X2ead     & 36.48913 &  -6.45118 & 20.08582 & 0.03290 & 0.23175 &      OzDES &       2.00000 \\
DES15C3edw     & 52.55235 & -27.71022 & 22.69331 & 0.03227 &    $^d$ &          - &             - \\
DES14S2plb     & 41.85667 &  -1.61811 & 18.38419 & 0.03463 & 0.11531 &      OzDES &       2.00000 \\
DES14S2pli     & 41.22837 &  -1.09830 & 20.86839 & 0.03093 & 0.35478 &      OzDES &       3.41667 \\
DES15X3kyt     & 36.27500 &  -5.41103 & 24.74520 & 0.07892 &    $^d$ &          - &             - \\
DES14C3tvw     & 53.32230 & -27.90621 & 21.31841 & 0.02516 & 0.70390 &       ACES &               \\
DES14C3tnz     & 52.86248 & -28.51318 & 22.26137 & 0.03386 & 0.70452 &      OzDES &       5.79361 \\
DES15X3mxf     & 36.74009 &  -5.23991 & 22.43347 & 0.04552 & 0.43673 &      OzDES &       9.83333 \\
DES15X3nlv     & 36.04464 &  -5.02735 & 25.26349 & 0.08375 &    $^d$ &          - &             - \\
DES15C3mem     & 52.14216 & -29.05851 & 20.28975 & 0.04590 & 0.61618 &     PRIMUS &               \\
DES15E2lmq     &  9.62005 & -43.98734 & 25.65868 & 0.18116 &    $^d$ &          - &             - \\
DES15C3lpq     & 52.71204 & -28.61319 & 23.28579 & 0.03610 & 0.61365 &      OzDES &       6.16667 \\
DES15C3lzm     & 52.17460 & -28.23186 & 20.47636 & 0.02573 & 0.32690 &      ATLAS &               \\
DES15C3nat     & 52.88528 & -28.72370 & 23.39015 & 0.03154 & 0.83929 &      OzDES &      18.62222 \\
DES15C3mgq     & 52.76901 & -28.20882 & 22.97470 & 0.03194 & 0.23031 &      OzDES &       8.16667 \\
DES15E2nqh     &  9.73174 & -43.08707 & 23.29709 & 0.03941 & 0.51525 &      OzDES &       6.83333 \\
DES15C3opk     & 51.66147 & -28.34737 & 23.05209 & 0.03270 & 0.56984 &      OzDES &      12.16667 \\
DES15C3opp     & 51.73962 & -28.11496 & 23.25950 & 0.04223 & 0.44242 &      OzDES &      16.75000 \\
DES15C3pbi     & 52.23620 & -28.00223 & 25.10028 & 0.05470 &    $^d$ &          - &             - \\
DES16E2pv      &  9.20875 & -43.52782 & 23.00100 & 0.05043 & 0.72608 &      OzDES &       6.00000 \\
DES16S1bbp     & 43.26389 &   0.37149 & 21.42883 & 0.04524 & 0.19018 &      OzDES &       3.33333 \\
DES15X3oma     & 36.74617 &  -5.11040 & 24.94606 & 0.07447 &    $^d$ &          - &             - \\
DES16C3bor     & 52.48232 & -28.04256 & 23.83923 & 0.03711 &    $^c$ &      OzDES &             - \\
DES16C1bde     & 54.30149 & -26.75840 & 24.96313 & 0.09485 &    $^d$ &          - &             - \\
DES16X3wt      & 36.23751 &  -5.54488 & 26.90234 & 0.28423 &    $^d$ &          - &             - \\
DES16X3cxn     & 36.83044 &  -4.95100 & 23.05257 & 0.04442 & 0.58464 &      OzDES &      12.83333 \\
DES16X2bke     & 36.00989 &  -7.27130 & 25.13096 & 0.16403 &    $^d$ &          - &             - \\
DES16C1cbd     & 54.85826 & -27.67254 & 20.93909 & 0.03048 & 0.54108 &      OzDES &       7.20000 \\
DES16C3cdd     & 52.42731 & -27.14317 & 24.27019 & 0.05040 &    $^d$ &          - &             - \\
DES16E1bir     &  7.74444 & -42.97696 & 24.74236 & 0.07595 &    $^c$ &      OzDES &             - \\
DES16C3auv     & 51.90215 & -27.59087 & 24.39158 & 0.05296 &    $^c$ &      OzDES &             - \\
DES16C3axz     & 52.80904 & -28.66678 & 20.41796 & 0.03716 & 0.22673 &  LADUMA &               \\
DES16X3ega     & 37.09820 &  -4.77643 & 19.53601 & 0.04874 & 0.25762 &       GAMA &       1.00000 \\
DES16X3erw     & 36.20545 &  -4.51438 & 22.23157 & 0.02865 & 0.45885 &      OzDES &       2.00000 \\
DES16X1ddm     & 33.82824 &  -4.36428 & 21.46049 & 0.04767 &    $^c$ &      OzDES &             - \\
DES16X3ddi     & 35.43936 &  -4.68602 & 23.93720 & 0.04360 &    $^c$ &      OzDES &             - \\
DES16C3gin     & 52.76276 & -28.29145 & 21.52696 & 0.03653 & 0.34745 &      OzDES &       3.33333 \\
DES16S1dxu     & 42.68141 &  -0.71039 & 21.35662 & 0.03193 & 0.13528 &      OzDES &       1.33333 \\
DES16X1eho     & 35.34537 &  -4.52566 & 22.28516 & 0.07277 & 0.80735 &      OzDES &       6.75000 \\
DES17X3gmp     & 37.40191 &  -4.65060 & 24.44397 & 0.06946 &    $^d$ &          - &             - \\
DES17X2dqk     & 35.46926 &  -7.10815 & 25.96184 & 0.19576 &    $^d$ &          - &             - \\
DES17C3gop     & 53.53574 & -28.40024 & 22.74858 & 0.03107 & 0.69185 &      OzDES &       4.00000 \\
DES17C3gen     & 52.93346 & -29.01119 & 22.79380 & 0.04204 &    $^c$ &      OzDES &             - \\
DES17X3fhq     & 35.93682 &  -3.97690 & 24.70876 & 0.05177 &    $^d$ &          - &             - \\
DES17S2fee     & 41.40953 &  -1.33278 & 18.16644 & 0.04681 & 0.23737 &      OzDES &       2.00000 \\
DES17X1hjj     & 34.24036 &  -4.21180 & 24.07284 & 0.05854 &    $^c$ &      OzDES &             - \\
DES17X1dge     & 34.80886 &  -5.40370 & 24.15755 & 0.10116 &    $^d$ &          - &             - \\
DES17C1fes     & 54.23372 & -27.57015 & 24.42015 & 0.10382 &    $^c$ &      OzDES &             - \\
DES17E1gsx     &  8.11588 & -42.76823 & 22.70982 & 0.04695 &    $^c$ &      OzDES &             - \\
DES17X3dxu     & 36.55911 &  -3.84432 & 22.83789 & 0.03973 & 0.85565 &      OzDES &       7.50000 \\
DES17S1emy     & 43.36298 &   0.41758 & 22.51310 & 0.05326 &    $^d$ &          - &             - \\
DES17X2cvk     & 35.93444 &  -7.32167 & 21.60107 & 0.06456 &    $^d$ &          - &             - \\
DES17X3cdp     & 37.28283 &  -4.30434 & 25.10651 & 0.08381 &    $^c$ &      OzDES &             - \\
DES17X3cds     & 36.27737 &  -3.79891 & 22.45168 & 0.06098 & 0.49444 &      OzDES &       5.50000 \\
DES17C3fwd     & 52.90461 & -27.46979 & 20.46182 & 0.02355 & 0.34561 &    LADUMA &               \\
DES17S1hih     & 42.57627 &  -0.76193 & 24.94967 & 0.12010 &    $^d$ &          - &             - \\
DES17C3fjt     & 51.46785 & -28.14106 & 28.04246 & 0.44157 &    $^d$ &          - &             - \\
DES17X3hxi     & 35.79624 &  -4.51713 & 23.36715 & 0.03375 & 0.62457 &      OzDES &       2.00000 \\
DES13E2lpk     & 10.09911 & -43.53903 & 20.49379 & 0.03567 & 0.47541 &      OzDES &       6.00000 \\
DES15C2eal     & 54.06180 & -29.23000 & 22.99891 & 0.03276 & 0.22347 &      OzDES &      16.90833 \\
DES16C2ggt     & 53.89079 & -29.22496 & 21.09210 & 0.03142 & 0.31057 &      OzDES &       2.66667 \\
DES16C2grk     & 55.06853 & -29.28963 & 20.45434 & 0.03869 &    $^d$ &          - &             - \\
DES17C2hno     & 53.72691 & -29.19742 & 22.69257 & 0.07398 & 0.59953 &      OzDES &       4.66667 \\
\begin{tablenotes}
\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
\item[c] Host targetted by OzDES but no redshift measurement possible.
\item[d] Host not targetted by OzDES
\item[e] Found by updated search method (Section \ref{subsec:new_method})
\item[f] Found in Season 5 using \citetalias{Pursiainen2018} method 
\end{tablenotes}
\end{threeparttable}
\label{tab:obs}

@@

\section{Sample selection}
\label{sec:sample}
We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey. This number expands upon the 72 of \citetalias{Pursiainen2018}. The first reason for the increased sample size is the use of the 5th year of DES-SN, where \citetalias{Pursiainen2018} were only able to make use of the first four years. \replylluis{By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.} The second reason is an update to the sample selection technique, \replylluis{which adds a further 14 transients.}

@@

Using the above method recovers 87 of the 92 RETs found using the \citetalias{Pursiainen2018} technique, and adds a further 14. The five were not recovered as their GP lightcurves were fainter than the limits given above in either g or r band.
We refer to the resulting sample as DES RETs. Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift \replychris{which we access through an internal release of the OzDES Global Redshift Catalog (GRC; v.2020\_01\_04). The full OzDES GRC will be available alongside the public data release detailed in \citet{Lidman2020}}. A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves. We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
\replylluis{A selection of the host galaxies can be seen in Fig. \ref{fig:mosaic}, centered on the location of the transient. The figure showcases the diversity of host galaxy morphologies and colours, while also displaying the limitations of ground-based observations of high-redshift, relatively small galaxies in terms of spatial resolution.}
Fig. \ref{fig:z_dist} shows the distribution of redshifts amongst the 49 hosts for which such a measurement was possible. The effect that the redshift selection function has on the results is discussed in Section \ref{subsec:disc_bias}.
The observational properties of the 9\replylluis{6} detected hosts are displayed in Table \ref{tab:obs}. We highlight objects that were not presented in \citetalias{Pursiainen2018}. We also highlight a small subset of objects for which the redshift has taken on a new value than that presented in \citetalias{Pursiainen2018} due to further OzDES observations leading to a more accurate determination.

@@

\section{Host galaxy observations}
\label{sec:obs}
\subsection{Photometry \label{subsec:phot}}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:sfms_sfr}}
\end{figure}

@@

The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised. Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the PP04 O3N2 scale using the conversion from \citet{Kewley2008}. This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available. For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we transform them all to the PP04 O3N2 scale. Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the probability density functions (PDFs) of the various different diagnostics \replylluis{scaled to PP04 O3N2}, resulting in a final `best' PDF. We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and \replylluis{for DES RETs} display the results in Table \ref{tab:derived}.

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
\caption{The sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:sfms_ssfr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/cum_sSFR_mike.png}
\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:ssfr_cum}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_OH_cum.png}
\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:oh_cum}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
\caption{The mass-metallicity relation (MZR) for RET host galaxies. \replylluis{Upward- and downward-pointing triangles reflect lower and upper limits respectively. The DES RETs with no metallicity measurement have been placed at the top of the figure for completeness.}
\label{fig:mzr}}
\end{figure}

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
%Co-authors:
\newcommand{\phil}[1]{\color{red}#1 \color{black}}
\newcommand{\mike}[1]{\color{cyan}#1 \color{black}}
\newcommand{\replychris}[1]{\color{magenta}#1 \color{black}}
\newcommand{\replylluis}[1]{\color{brown}#1 \color{black}}
\newcommand{\comment}[1]{\textbf{[#1]}} %comments

@@

 Along with observations of the transients themselves, host galaxies are frequently-used laboratories from which strong inferences about the progenitor stars and explosion mechanisms can be made. CCSNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars. There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties. On average, SESNe reside in galaxies with higher specific star-formation rate\replychris{s} (sSFRs; \citealt{James2006,Kelly2008}), \replylluis{while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Galbany2018}}. More extreme events tend to occur in galaxies low in mass and high in sSFR, with both GRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.

@@

The order of the paper is as follows: \replychris{in Section \ref{sec:sample} we introduce the full DES RET sample and describe the host galaxy observations in Section \ref{sec:obs}. The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:disc}) and conclusion (Section \ref{sec:conc}).}
Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters H$0=70$ km~s$^{-1}$ and $\Omega_{\textrm{M}}=0.3$. Magnitudes are presented in the AB system \citep{Oke1983}.

@@

DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    $^c$ &      OzDES &             - \\
DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.58333 \\
DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.19647 &      OzDES &      10.16667 \\
DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    $^d$ &          - &             - \\
DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.56985 &      OzDES &       5.41639 \\
DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.00000 \\
DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    $^c$ &      OzDES &             - \\
DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.50000 \\
DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.91667 \\
DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.34577 &  LADUMA &               \\
DES13X3afjd    & 37.00386 &  -4.58049 & $20.75 \pm 0.05$ &    $^d$ &          - &             - \\
DES13C1acmt    & 54.32925 & -26.83371 & $23.18 \pm 0.04$ &    $^c$ &      OzDES &             - \\
DES13X3kgm     & 36.50380 &  -4.86636 & $26.46 \pm 0.18$ &    $^d$ &          - &             - \\
DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.67346 &       ACES &               \\
DES13C3nxi     & 51.96356 & -28.35720 & $24.99 \pm 0.05$ &    $^c$ &      OzDES &             - \\
DES13C3asvu    & 52.83670 & -27.36071 & $22.46 \pm 0.02$ &    $^d$ &          - &             - \\
DES13X3pby     & 36.33330 &  -5.31408 & $23.82 \pm 0.04$ &    $^c$ &      OzDES &             - \\
DES13X3aakf    & 35.71205 &  -4.69915 & $25.47 \pm 0.09$ &    $^c$ &      OzDES &             - \\
DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.50000 \\
DES13X2oyb     & 35.31056 &  -5.67893 & $22.91 \pm 0.06$ &    $^c$ &      OzDES &             - \\
DES13X3alnb    & 37.18496 &  -5.14232 & $25.04 \pm 0.06$ &    $^c$ &      OzDES &             - \\
DES15X3atd     & 35.84011 &  -4.29142 & $23.87 \pm 0.05$ &    $^c$ &      OzDES &             - \\
DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75000 \\
DES14E2xsm     &  9.67624 & -43.58736 & $23.39 \pm 0.04$ &    $^c$ &      OzDES &             - \\
DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.50000 \\
DES14E1aqi     &  8.73970 & -43.40182 & $25.61 \pm 0.23$ &    $^d$ &          - &             - \\
DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.33333 \\
DES14C3gzj     & 52.57168 & -28.14019 & $26.04 \pm 0.10$ &    $^d$ &          - &             - \\
DES14X3pko     & 36.90824 &  -3.69642 & $24.48 \pm 0.06$ &    $^d$ &          - &             - \\
DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.66667 \\
DES14C1jnd     & 54.35153 & -27.49300 & $24.33 \pm 0.08$ &    $^c$ &      OzDES &             - \\
DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.16667 \\
DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.16667 \\
DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.00000 \\
DES15C3edw     & 52.55235 & -27.71022 & $22.69 \pm 0.03$ &    $^d$ &          - &             - \\
DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.00000 \\
DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.41667 \\
DES15X3kyt     & 36.27500 &  -5.41103 & $24.74 \pm 0.07$ &    $^d$ &          - &             - \\
DES14C3tvw     & 53.32230 & -27.90621 & $21.31 \pm 0.02$ & 0.70390 &       ACES &               \\
DES14C3tnz     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.79361 \\
DES15X3mxf     & 36.74009 &  -5.23991 & $22.43 \pm 0.04$ & 0.43673 &      OzDES &       9.83333 \\
DES15X3nlv     & 36.04464 &  -5.02735 & $25.26 \pm 0.08$ &    $^d$ &          - &             - \\
DES15C3mem     & 52.14216 & -29.05851 & $20.28 \pm 0.04$ & 0.61618 &     PRIMUS &               \\
DES15E2lmq     &  9.62005 & -43.98734 & $25.65 \pm 0.18$ &    $^d$ &          - &             - \\
DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.16667 \\
DES15C3lzm     & 52.17460 & -28.23186 & $20.47 \pm 0.02$ & 0.32690 &      ATLAS &               \\
DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.62222 \\
DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.16667 \\
DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.83333 \\
DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.16667 \\

\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
\item[c] Host targetted by OzDES but no redshift measurement possible.
\item[d] Host not targetted by OzDES
\item[e] Found by updated search method (Section \ref{subsec:new_method})
\item[f] Found in Season 5 using \citetalias{Pursiainen2018} method 
\end{tablenotes}
\end{threeparttable}
\label{tab:obs}
\end{table*}

@@

\section{Sample selection}
\label{sec:sample}
We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey. This number expands upon the 72 of \citetalias{Pursiainen2018}. The first reason for the increased sample size is the use of the 5th year of DES-SN, where \citetalias{Pursiainen2018} were only able to make use of the first four years. \replylluis{By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.} The second reason is an update to the sample selection technique, \replylluis{outlined in the following subsection, which adds a further 14 transients.}

@@

Using the above method recovers 87 of the 92 RETs found using the \citetalias{Pursiainen2018} technique, and adds a further 14. The five were not recovered as their GP lightcurves were fainter than the limits given above in either g or r band.
We refer to the resulting sample as DES RETs. Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020} when using the Directional Light Radius method \citep{Sullivan2006} to associate hosts as per \citet{Wiseman2020}. Of these, 49 have a host galaxy spectroscopic redshift \replychris{which we access through an internal release of the OzDES Global Redshift Catalog (GRC; v.2020\_01\_04). The full OzDES GRC will be available alongside the public data release detailed in \citet{Lidman2020}}. A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves. We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
\replylluis{A selection of the host galaxies can be seen in Fig. \ref{fig:mosaic}, centered on the location of the transient. The figure showcases the diversity of host galaxy morphologies and colours, while also displaying the limitations of ground-based observations of high-redshift, relatively small galaxies in terms of spatial resolution.}
Fig. \ref{fig:z_dist} shows the distribution of redshifts amongst the 49 hosts for which such a measurement was possible. The effect that the redshift selection function has on the results is discussed in Section \ref{subsec:disc_bias}.
The observational properties of the 9\replylluis{6} detected hosts are displayed in Table \ref{tab:obs}. We highlight objects that were not presented in \citetalias{Pursiainen2018}. We also highlight a small subset of objects for which the redshift has taken on a new value than that presented in \citetalias{Pursiainen2018} due to further OzDES observations leading to a more accurate determination.

@@

\subsection{Field Galaxies \label{subsubsec:sdss}}

\phil{To show how RETs compare to the galaxy population as a whole, we use the MPA-JHU catalogues of stellar masses (based off the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}). The mean redshift is 0.08 which is much lower than for the RETs, such that significant evolution in the galaxy population has happened between the majority of RET hosts and the SDSS sample. We do not correct for this, but take it into account when analysing our findings. }
\section{Host galaxy observations}
\label{sec:obs}
\subsection{Photometry \label{subsec:phot}}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
\caption{The $M_*$ - SFR sequence of RET hosts, \phil{hosts of other transients, and SDSS field galaxies. Transient SFRs have not been corrected for redshift evolution. RET hosts lie slightly above the low-$z$ star-formation main sequence.}
\label{fig:sfms_sfr}}
\end{figure}

@@

The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised. Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the PP04 O3N2 scale using the conversion factors given in \citet{Kewley2008}. This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available. For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we transform them all to the PP04 O3N2 scale. Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the probability density functions (PDFs) of the various different diagnostics \replylluis{scaled to PP04 O3N2}, resulting in a final `best' PDF. We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and \replylluis{for DES RETs} display the results in Table \ref{tab:derived}.

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
\caption{The sSFR of RET hosts and comparison samples, along with the SDSS field galaxies.
\label{fig:sfms_ssfr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/cum_sSFR_mike.png}
\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample. Uncertainties have been estimated via a bootstrap Monte-Carlo technique and include limits.
\label{fig:ssfr_cum}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_OH_cum.png}
\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, hosts of the comparison samples, and the SDSS sample. Uncertainties have been estimated via a bootstrap Monte-Carlo technique and include limits.
\label{fig:oh_cum}}
\end{figure}
